\documentclass[12pt, a4paper]{article}
\usepackage{ctex}
\usepackage{graphicx}
\usepackage{float}
\usepackage[super, square]{natbib}
\usepackage{booktabs}
\usepackage[margin = 1in]{geometry}
\usepackage{
  color,
  clrscode,
  amssymb,
  ntheorem,
  amsmath,
  listings,
  fontspec,
  xcolor,
  supertabular,
  multirow
}
\renewcommand\contentsname{Contents}
\renewcommand\refname{References}
\definecolor{bgGray}{RGB}{36, 36, 36}
\usepackage[
  colorlinks,
  linkcolor=bgGray,
  anchorcolor=blue,
  citecolor=black
]{hyperref}
\newfontfamily\courier{Courier}

\theoremstyle{margin}
\theorembodyfont{\normalfont}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\newcommand{\st}{\text{s.t.}}
\newcommand{\mn}{\mathnormal}
\newcommand{\tbf}{\textbf}
\newcommand{\fl}{\mathnormal{fl}}
\newcommand{\f}{\mathnormal{f}}
\newcommand{\g}{\mathnormal{g}}
\newcommand{\R}{\mathbf{R}}
\newcommand{\Q}{\mathbf{Q}}
\newcommand{\JD}{\textbf{D}}
\newcommand{\rd}{\mathrm{d}}
\newcommand{\str}{^*}
\newcommand{\vep}{\varepsilon}
\newcommand{\lhs}{\text{L.H.S}}
\newcommand{\rhs}{\text{R.H.S}}
\newcommand{\con}{\text{Const}}
\newcommand{\oneton}{1,\,2,\,\dots,\,n}
\newcommand{\aoneton}{a_1a_2\dots a_n}
\newcommand{\xoneton}{x_1,\,x_2,\,\dots,\,x_n}

\title{Project Report of RISC-V CPU\\\begin{large}(Course Project of Computer Architecture)\end{large}}
\author{Zhou Fan (范舟)\\ACM Class, Shanghai Jiao Tong University}
\date{}

\begin{document}

\lstset{numbers=left,
  basicstyle=\scriptsize\courier,
  numberstyle=\tiny\courier\color{red!89!green!36!blue!36},
  language=C++,
  breaklines=true,
  keywordstyle=\color{blue!70},commentstyle=\color{red!50!green!50!blue!50},
  morekeywords={},
  stringstyle=\color{purple},
  frame=shadowbox,
  rulesepcolor=\color{red!20!green!20!blue!20}
}
\maketitle

\section{Introduction}

GitHub repository of my CPU project: \url{https://github.com/Evensgn/RISC-V-CPU}

This project is a RISC-V CPU with five-stage pipeline, implemented in Verilog HDL. 

\section{Design}

% Please add the following required packages to your document preamble:
% 
\begin{table}[H]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\multicolumn{1}{c}{Feature} & \multicolumn{1}{c}{RISC-V CPU}                                                                        \\ \midrule
ISA                         & RISC-V (\href{https://github.com/Evensgn/RISC-V-CPU/blob/dev/doc/inst-supported.md}{RV32I subset}) \\
Pipelining                  & 5 stages                                                                                              \\
Data forwarding             & complete forwarding path                                                                              \\
Cache                       & N-way set associate I-cache and D-cache                                 \\ \bottomrule
\end{tabular}
\end{table}

\begin{itemize}
	\item 
	\item 
\end{itemize}

\section{Discusstion}

\section{Acknowledgements}

Special thanks would go to Zhanghao Wu (吴章昊) for his instructive discusstions and useful suggestions on this project. I would like to express my gratitude to TA Zhekai Zhang (张哲恺) as well, for his MIPS CPU project (especially the code of cache and UART module) and much work for this assignment. I am also indebted to many other classmates for their direct and indirect help to me.

\begin{thebibliography}{9}
  \bibitem{lsl}
  	雷思磊.
  	\emph{自己动手写CPU},
  	电子工业出版社, 2014.
  \bibitem{caqa} 
	John L. Hennessy, David A. Patterson, et al.
	\emph{Computer Architecture: A Quantitative Approach},
	Fifth Edition, 2012.
  \bibitem{ppt}
	David A. Patterson.
	PPT of \emph{CS252 Graduate Computer Architecture},
	2001.
  \bibitem{zzk}
  	Zhekai Zhang's (张哲恺) MIPS CPU project.
  	\url{https://github.com/sxtyzhangzk/mips-cpu}
  \bibitem{always}
  	Chris Fletcher.
  	\emph{Verilog: always @ Blocks}
  	\url{https://github.com/Evensgn/RISC-V-CPU/blob/dev/doc/Always@.pdf}
  
\end{thebibliography}

\end{document}